Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2020-09-04 journal paper/content/conclusion.tex
Minor edits.

\item \emph{Horizontal differentiation.}
Horizontally differentiated user preferences may help explain how competition may encourage specialization, \ie how the firms may \emph{learn to specialize} under competition.

\item \emph{Continuous learning.}
While we focus on learning from scratch in a mainly stationary world, another well-motivated regime is continuous learning, when exploration counteracts change
\citep{DynamicMAB-colt08}.
The economic story would be about competition between relatively mature firms.

>>>>

\item 
\emph{Horizontally differentiated} user preferences may help explain how competition may encourage specialization, \ie how the firms may \emph{learn to specialize} under competition.

\item \emph{Continuous learning.}
While we focus on a stationary world, another well-motivated regime is continuous learning, when exploration counteracts change
\citep{DynamicMAB-colt08}.
The economic story would be about competition between relatively mature firms.
